DisCon Kids Pilot

### 2019-02-20 analysis/01_adult_speakerchange_preference.Rmd
update kids analysis

ggplot() +
  geom_jitter(data = plot3, aes(x = speakerChange, y = prop_correct, col = speakerChange, alpha = .2), width = .3,height = .025)+
  geom_pointrange(data = plot3a, aes(x = speakerChange, y = mean, col = speakerChange, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Speaker Change", y="Correct Item Chosen")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F) +
scale_colour_solarized(name = "Speaker Change",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))

>>>>

ggplot() +
  geom_jitter(data = plot3, aes(x = speakerChange, y = prop_correct, col = speakerChange, alpha = .2), width = .3,height = .025)+
  geom_pointrange(data = plot3a, aes(x = speakerChange, y = mean, col = speakerChange, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Speaker Change", y="Correct Item Chosen")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F) +
  scale_colour_solarized(name = "Speaker Change",
                       breaks = c("change", "same"),
                       labels = c("Different Speaker", "Same Speaker"))

### 2019-02-20 analysis/02_kids_600.Rmd
update kids analysis

# linking the data to the demographics spreadsheet
# always check if subjects get "lost" due do differetn subids
log <- read_excel("../../DisCon-subject_log.xlsx", 1)%>%
  filter(Condition == "d600")%>%
  mutate(dob = as.Date(dob))%>%
  select(subid,experimenter,keep_drop,sex,dob)

@@

@@

```{r proportion of choices}
p1 <- data %>%
  filter(phase == 'test')%>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct_target1))

p2 <- p1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p1, aes(x = subage, y = correct, col = subage, alpha = .2),width = .1,height = .025)+
  geom_pointrange(data = p2, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct in training")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

@@

```{r}
p3 <- data %>%
  filter(phase == 'test')%>%
  group_by(age_num, subid) %>%
  summarise(correct = mean(correct_target1))

ggplot(data = p3, aes(x = age_num, y = correct)) +
  geom_jitter(width = .0,height = .0, alpha = .5)+
  geom_smooth(method = "lm",  se = T,  alpha = .5, size = .6, span = 2)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Age",y="Proportion correct choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F)
```

>>>>

# linking the data to the demographics spreadsheet
# always check if subjects get "lost" due do differetn subids
log <- read_excel("../../DisCon-subject_log.xlsx", 1)%>%
  filter(Condition == "d600")%>%
  mutate(dob = as.numeric(dob),
         dob = as.Date(dob,origin = "1899-12-30"))%>%
  select(subid,experimenter,keep_drop,sex,dob)

@@

# Proportion correct choice in test trials across age bins

```{r proportion of choices}
p1 <- data %>%
  filter(phase == 'test')%>%
  group_by(experiment,subid) %>%
  summarise(correct = mean(correct_target1))

p2 <- p1 %>%
  group_by(experiment) %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p1, aes(x = experiment, y = correct,  alpha = .2),width = .2,height = .01)+
  geom_pointrange(data = p2, aes(x = experiment, y = mean,  ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct in training")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

@@

```{r proportion of choices}
p3 <- data %>%
  filter(phase == 'test')%>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct_target1))

p4 <- p1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p3, aes(x = subage, y = correct, col = subage, alpha = .2),width = .2,height = .01)+
  geom_pointrange(data = p4, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct in training")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

@@

```{r}
p5 <- data %>%
  filter(phase == 'test')%>%
  group_by(age_num, subid) %>%
  summarise(correct = mean(correct_target1))

ggplot(data = p5, aes(x = age_num, y = correct)) +
  geom_jitter(width = .0,height = .0, alpha = .5)+
  geom_smooth(method = "lm",  se = T,  alpha = .5, size = .6, span = 2)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Age",y="Proportion correct choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F)
```
